Make any stupid plot you want

### 2021-01-19 draft/sections/math.tex
next section

We also add the variable name and measurement scale $M$ monoid to the fiber $F_i$ such that 
\begin{align}
    $F_0$ &= (\mathrm{temperature}, \text{Temp}, $M_0$)\\
    $F_1$ &= (\mathrm{time}, \text{Time}, $M_1$)\\
    $F_2$ &= (\mathrm{location}, \text{Loc}, $M_2$)
\end{align}

as described in Spivak's categorical formulation of databases \cite{spivakSIMPLICIALDATABASES}. We describe $M$ in more detail in section~\ref{sec:data_monoid}. We can keep growing the fiber
\begin{equation}
F= F_{0} \times \ldots \times F_{n}
\end{equation}
while also retaining the individual sets $F_{i}$ that we will later apply visual variables to.

>>>>

We also add the variable name and measurement scale $M$ monoid to the fiber $F_i$ such that 
\begin{align}
    F_0 &= (\mathrm{temperature}, \text{Temp}, M_0)\\
    F_1 &= (\mathrm{time}, \text{Time}, M_1)\\
    F_2 &= (\mathrm{location}, \text{Loc}, M_2)
\end{align}
 or more generally (name, set, monoid)
 \begin{equation}
    F_i = (\mathrm{name}, \{x_{i}, \ldots, \x_{n}\}, M_{i})
 \end{equation}
as described in Spivak's categorical formulation of databases \cite{spivakSIMPLICIALDATABASES}. We describe $M$ in more detail in section~\ref{sec:data_monoid}. We can keep growing the fiber
\begin{equation}
F= F_{0} \times \ldots \times F_{n}
\end{equation}
while also retaining the individual sets $F_{i}$ that we will transform into visual characteristics of the graphic.
